### 2020-05-31 fig/diagram.tex
changes
ready to submit

\node(local)[bigcompartment, right=3.4cm of int, text width=5cm, fill opacity=0.7, text opacity=1]{
    \textbf{Realized GI}
    \footnotesize{
        \begin{itemize}
        	\item time distribution between actual infection events
        	\item egocentric depletion, local depletion, global depletion
        \end{itemize}
    }
};

@@

\node(agg)[bigcompartment, right=3.4cm of local, text width=5cm, fill opacity=0.7, text opacity=1]{
    \textbf{Aggregated GI}
    \footnotesize{
        \begin{itemize}
        	\item analogous to contact tracing data
        	\item truncated at epidemic time
        \end{itemize}
    }
};

\node(iniagg)[bigcompartment, below=1.61cm of agg, text width=5cm, fill opacity=0.7, text opacity=1]{
    \textbf{Initial aggregated GI}
    \footnotesize{
        \begin{itemize}
        	\item aggregated GI during the exponential growth phase
        	\item truncation bias is understood exactly
        \end{itemize}
    }
};
\draw[->, very thick, dashed] (int) -- node [midway, left, text width=2cm, align=right] {} (local);
\draw[->, very thick, dashed] (local) -- node [midway, right, text width=2cm] {exponential growth \\ phase} (forward);
\draw[->, very thick, dashed] (local) -- node [midway, right, text width=2cm] {} (agg);
\draw[->, very thick, dashed] (agg) -- node [midway, right, text width=2cm] {exponential growth \\ phase} (iniagg);
\draw[->, very thick] (iniagg) -- node [midway, above, text width=1.5cm] {temporal \\ correction} (forward);

>>>>

\node(local)[bigcompartment, right=3.4cm of int, text width=5cm, fill opacity=0.7, text opacity=1]{
    \textbf{Realized GI}
    \footnotesize{
        \begin{itemize}
        	\item time distribution between actual infection events
        	\item subject to egocentric, local, and global depletion
        \end{itemize}
    }
};

@@

\node(agg)[bigcompartment, right=3.4cm of local, text width=5cm, fill opacity=0.7, text opacity=1]{
    \textbf{Aggregated GI}
    \footnotesize{
        \begin{itemize}
        	\item contact tracing data
        	\item truncated at observation time
        \end{itemize}
    }
};

\node(iniagg)[bigcompartment, below=1.61cm of agg, text width=5cm, fill opacity=0.7, text opacity=1]{
    \textbf{Initial aggregated GI}
    \footnotesize{
        \begin{itemize}
        	\item measured during the exponential growth phase
        \end{itemize}
    }
};
\draw[->, very thick, dashed] (int) -- node [midway, left, text width=2cm, align=right] {} (local);
\draw[->, very thick, dashed] (local) -- node [midway, right, text width=2cm] {exponential growth \\ phase} (forward);
\draw[->, very thick, dashed] (local) -- node [midway, above, text width=2cm] {truncation \\ bias} (agg);
\draw[->, very thick, dashed] (agg) -- node [midway, right, text width=2cm] {exponential growth \\ phase} (iniagg);
\draw[->, very thick] (iniagg) -- node [midway, above, text width=1.5cm] {temporal \\ correction} (forward);
